Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory

### 2019-10-04 paper2_JNLS/paper.tex
NM

>>>>

We now introduce the theoretical framework that will be used to understand and quantify the experimental observations. This framework is based on a Galerkin truncation of the variable-depth Korteweg–de Vries (KdV) equation. The KdV equation is a commonly excepted model for describing the propagation of unidirectional, shallow-water waves, accounting for weak nonlinearity and weak dispersion over long timescales and large spatial scales. We will perform Galerkin truncation of this system at wavenumber $\Lambda = $8--32 to obtain a finite dimensional dynamical system exhibiting weak turbulence. We outline the Hamiltonian structure of both the continuous KdV and the truncated system. This structure is exploited to obtain invariant measures of the underlying dynamics and to ultimately understand the experimental findings on anomalous wave statistics triggered by an ADC.
